---
title: "Creation d'un Package"
output: html_document
---


#### Libraries nécessaires

```{r Installation, eval=F}
install.packages(c("devtools", "roxygen2", "testthat", "knitr"))
library(devtools)
has_devel()
```

La dernière commande teste si vous possédez tous les outils nécessaires. La réponse doit être TRUE. Si ce n’est pas le cas :  
- On Windows, download and install Rtools. NB: this is not an R package!  
- On Mac, make sure you have either XCode (available for free in the App Store) or the “Command Line Tools for Xcode”. NB: you’ll need to have an Apple ID (available for free).  
- On Linux, make sure you’ve installed not only R, but also the R development tools. For example, on ubuntu (and debian) you need to install the r-base-dev package.  


#### Création de l’architecture en dossier/ sous-dossiers

```{r, eval=F}
devtools::create("~/Desktop/Package/PermPSDRF")
```
La commande précédente crée un dossier dénommé PermPSDRF situé sur le bureau dans le dossier Package et contenant 4 éléments  
- An RStudio project file, pkgname.Rproj.  
- An R/ directory.  
- A basic DESCRIPTION file.  
- A basic NAMESPACE file.  

To get started with your new package in RStudio, double-click the package.Rproj  


#### Stockage des data
```{r, eval=F}
setwd("~/Documents/GeoData/FRA_adm")
dept <- readOGR(dsn=".", layer="Dept25")
setwd("~/Desktop/Package")
ser <- readOGR(dsn="SIG/Vecteurs", layer="ser25_l93")
setwd("PermPSDRF")
devtools::use_data(ser,dept, overwrite = T)
```


```{r}
devtools::load_all()
```


#### Conventions
If you’re planning on submitting your package to CRAN, you must use only ASCII characters in your .R files. Il faut pour cela utiliser la fonction stri_escape_unicode qui se trouve dans le package stringi 
```{r}
cat(stringi::stri_escape_unicode("surface terrière"))
```

